Software Architectures for Integrating Workflow Engines in Science Gateways

### 2016-05-03 paper.tex
Added acknowledgments to Brain Canada PSG as well as CCNA.
Updates in abstract (#17)

\title{An analysis of existing software architectures\\ to integrate workflow engines in science gateways\closednote{Naj}{'what' software architectures? what is their qualifier, adjective?}{Tristan}{There is no qualifier except 'for integrating workflow engines in science gatewats'. They are just software architectures :) The point of the paper is to describe them properly. It's a general formulation to cover any kind of software architecture that is used to integrated workflow engines in science gateways. Does it make sense?}}

@@

\begin{abstract}
  We investigate six software architectures commonly used to integrate
  workflow engines in science gateways. We describe and evaluate these
  architectures with metrics that measure integration complexity,
  robustness, extensibility, scalability and support for
  meta-workflows and fine-grained debugging\closednote{Naj}{Please be
    precise, what are they?}{Tristan}{Done, thanks}. Results
  illustrate the pros and cons of different architectures: Tight
  integration and task encapsulation are the easiest to integrate and
  are most robust. Extensibility is equivalent in most
  architectures. The pool model is the most scalable one and
  meta-workflows are only available in nested workflows and workflow
  import. Our analysis provides insights for science gateway
  architects and workflow engine developers. \note{Naj}{I find this
    abstract to be vague, it can be made more concise and poignant}
\end{abstract}

@@

This work is in the scope of the LABEX PRIMES (ANR-11- LABX-0063) of
Universit\'e de Lyon, within the program ``Investissements d’Avenir''
(ANR-11-IDEX-0007) operated by the French National Research Agency
(ANR). This work also falls into the scope of the scientific topics of
the French National Grid Institute (IdG). We thank the site
administrators of the European Grid Initiative and the GGUS support
for their help related to the VIP platform. The CBRAIN team is grateful for the
computing cycles, storage, and support obtained from Compute Canada
(\url{https://computecanada.ca}) and platform development program from CANARIE
 (\url{http://www.canarie.ca/}). This work has been made possible with the support of the Irving Ludmer Family Foundation and
the Ludmer Centre for Neuroinformatics and Mental Health. \closedanswerednote{Marc-e}{Would it be proper to thank EGI?
  Compute Canada? CANARIE?}{Tristan}{Added EGI and Compute Canada. Not sure if
  Canarie should be added. What about Calcul QC?}{Marc-e}{CQ, no. CANARIE, I'd
  say yes since they funded a major chunk of CBRAIN's development.}

>>>>

\title{A comprehensive analysis of existing software architectures\\ to integrate workflow engines in science gateways\closednote{Naj}{'what' software architectures? what is their qualifier, adjective?}{Tristan}{There is no qualifier except 'for integrating workflow engines in science gatewats'. They are just software architectures :) The point of the paper is to describe them properly. It's a general formulation to cover any kind of software architecture that is used to integrated workflow engines in science gateways. Does it make sense?}}

@@

\begin{abstract}
  We investigate six software architectures commonly used to integrate
  workflow engines in science gateways. (1) In \emph{tight
    integration}, the workflow engine shares software components with
  the science gateway; (2) In \emph{service invocation}, the engine is
  isolated and invoked through a specific software interface; (3) In
  \emph{task encapsulation}, the engine is wrapped as a computing task
  executed on the infrastructure; (4) In the \emph{pool model}, the
  engine is bundled in an agent that connects to a central pool to
  fetch and execute workflows; (5) In \emph{nested workflows}, the
  engine is integrated as a child process of another engine; (6) In
  \emph{workflow import}, the engine is integrated through workflow
  language conversion. We describe and evaluate these architectures
  with metrics that measure integration complexity, robustness,
  extensibility, scalability and support for meta-workflows and
  fine-grained debugging\closednote{Naj}{Please be precise, what are
    they?}{Tristan}{Done, thanks}. Results provide insights for
  science gateway architects and workflow engine developers. Tight
  integration and task encapsulation are the easiest to integrate and
  are most robust. Extensibility is equivalent in most
  architectures. The pool model is the most scalable one and
  meta-workflows are only available in nested workflows and workflow
  import. \note{Naj}{I find this abstract to be vague, it can be made
    more concise and poignant}
\end{abstract}

@@

This work is in the scope of the LABEX PRIMES (ANR-11- LABX-0063) of
Universit\'e de Lyon, within the program ``Investissements d’Avenir''
(ANR-11-IDEX-0007) operated by the French National Research Agency
(ANR). This work also falls into the scope of the scientific topics of
the French National Grid Institute (IdG). We thank the site
administrators of the European Grid Initiative and the GGUS support
for their help related to the VIP platform. The CBRAIN team is grateful for the
computing cycles, storage, and support obtained from Compute Canada
(\url{https://computecanada.ca}) and platform development program from CANARIE
 (\url{http://www.canarie.ca/}). The integration between PSOM and CBRAIN was supported by a Brain 
Canada Platform Support Grant, as well as the Canadian Consortium on
Neurodegeneration in Aging (CCNA), through a grant from the Canadian Institute
of Health Research and funding from several partners. This work has been made possible with the support of the Irving Ludmer Family Foundation and
the Ludmer Centre for Neuroinformatics and Mental Health. \closedanswerednote{Marc-e}{Would it be proper to thank EGI?
  Compute Canada? CANARIE?}{Tristan}{Added EGI and Compute Canada. Not sure if
  Canarie should be added. What about Calcul QC?}{Marc-e}{CQ, no. CANARIE, I'd
  say yes since they funded a major chunk of CBRAIN's development.}
